\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-08 paper/main.tex
wrote onion comment functionalities section

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
%Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{snippets/snippet1.pdf}
\caption{\small \textbf{FILL THIS IN...}}
\label{fig:snippet1}
\end{figure}

Onion comments are also useful for smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples). However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will search for the smuggled package in the local environment (as usual), and if it is found, further check whether the existing version satisfies the given constraint(s). If either check fails, \texttt{davos} will install and use a suitable version of the package (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).

>>>>

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippet1})} (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples). 
%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippet1}.
%Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by

Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_). However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead. Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).

%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version. If the installed version doesn't satisfy the given constraint (or if no local version is found), \texttt{davos} will install and load a suitable version instead. This guarantees the notebook is always run with a specific (or constrained) version of a particular package. Similarly, \texttt{davos} 
%If the package exists locally, \texttt{davos} will extract its version from metadata before loading it to determine its version, and if it does not match the requested version (or if no local installation is found), 
%If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will check whether the smuggled package is installed locally (as usual), and if so, additionally parse its metadata to determine 
%Adding a version specifier \cite{CoghStuf13} to an onion comment guarantees the version loaded into the notebook will matches the version specified

\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_). For example, \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to \texttt{pip}'s; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to \texttt{sys.path}, if necessary, so the package can be imported.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{snippets/snippet1.pdf}
\caption{\small Example \texttt{smuggle} statements and accompanying onion comments.}
\label{fig:snippet1}
\end{figure}
